---
title:  "GWAS Pipeline Full"
author: "Michael Beyeler"
date:   "2018-05-13"
output:
  # html_document:
  # html_notebook
  rmarkdown::github_document
  # pdf_document:
    # code_folding: show
editor_options:
 chunk_output_type: inline
---



# Setup

## Loading packages, reproducibility

**Concerning reproducibility**: In order to guarantee reproducibility, keep the `.BuildReproducibleEnvironment(...)` FUNCTION active.

```{r loading packages and reproducibility, echo=FALSE, message=FALSE}

.LIST.OF.PACKAGES <- c(
  'data.table',           #
  'icesTAF',              # dos2unix function
#  'lintr',                # good debugging tool
  'lme4',                 # 
  'reticulate',           # required to switch between R and python chunks, apparently
  'tictoc'                # 
)


source('Helper_Scripts/Environment_Manipulation_and_Reproducibility.R')


# In order to make the script 100% reproducible, run_reproducible has to be set to TRUE
run_reproducible <- as.logical(commandArgs(trailingOnly=TRUE)[5])
if (run_reproducible == TRUE)
  .build_reproducible_environment(PROJECT.SNAPSHOT.DATE = "2018-05-16",
                                  PROJECT.VERSION       = "3.4.3",
                                  SCAN.FOR.PACKAGES     = TRUE)

.load_packages(.LIST.OF.PACKAGES)

```


## Checkpoint ans session info

```{r session info}
cat("The current checkpoint is:\n")
checkpoint::setSnapshot()
cat("\n\nSession Info:\n\n")
sessionInfo()
```



# Constants

```{r}

SEXUAL.DIMORPHISM            <- TRUE
PHENOTYPE.NAME               <- commandArgs(trailingOnly=T)[1]
SEX                          <- commandArgs(trailingOnly=T)[2]
NORMALITY.SIGNIFICANCE.LEVEL <- 0.05
INVERSIONS.CONSIDERED        <- c('In.2L.t', 'In.2R.NS', 'In.3R.P', 'In.3R.K', 'In.3R.Mo')

MAF.THRESHOLD                <- commandArgs(trailingOnly=T)[3]


# GWAS Constants

NUMBER_OF_PERMUTATIONS       <- commandArgs(trailingOnly=T)[4]
                              # commandArgs(trailingOnly=T)[5] is found above in reproducibility
USE_OFFICIAL_GSM             <- commandArgs(trailingOnly=T)[6]

OUTPUT_NAME                  <- paste('GWAS', PHENOTYPE.NAME, SEX, sep='_')
PHENOTYPE_DATA               <- paste('Inputs/Fast-Lmm-Input-', PHENOTYPE.NAME, '-', SEX, '.txt', sep='')
VARIANTS_TO_TEST             <- 'Inputs/Current_Pipeline_Variants'

fwrite(list(NUMBER_OF_PERMUTATIONS, OUTPUT_NAME, PHENOTYPE_DATA, VARIANTS_TO_TEST, USE_OFFICIAL_GSM),
       file='Inputs/GWAS_Constants.txt', sep="\n")
```



# Data and other Inputs

## Data

```{r}
# Main data

Phenotype_Raw <- read.delim(paste('Inputs/',PHENOTYPE.NAME,'_Phenotype_Full.txt', sep=""), header=T)

# Supporting data

Dgrp2_Inversions <- read.csv('Raw_Data/inversion.csv', header=T)
Dgrp2_Infection <- read.csv('Raw_Data/wolbachia.csv')

# Some phenotypes actually use the flystock ID instead of the DGRP ID.
# For these cases, this data frame will come in handy.
# Dgrp_Flystock_Ids <- read.delim('Raw_Data/Dgrp-Flystocks-Ids.txt',
#                                 comment.char='#')
```


## Functions

Functions that were specifically programmed for this script

```{r functions}

source('Functions/NormalityHistogram.R')
source('Functions/ChisqForNormality.R')
source('Functions/WriteBare.R')
```



## Phenotype adjustment procedure

```{r, echo=FALSE}
source("Scripts/Phenotype_Adjustment.R")
```



# Filtering Lines and Low Minor Allele Frequencies

At the moment, bash is causing some trouble in Windows R Markdown. Thus, in the meantime, I'm using a workaround to write a bash shell script using R code, and then executing it in an unix environment.

```{r}
cat(paste("#!/bin/bash

PHENOTYPE_NAME=", PHENOTYPE.NAME,"
MAF=", MAF.THRESHOLD,"

cd plink2_linux_x86_64
./plink2 --bfile ../Raw_Data/dgrp2 --keep ../Inputs/Plink-Lines-$PHENOTYPE_NAME.txt --maf $MAF --make-bed --out ../Inputs/Current_Pipeline_Variants
", sep=''),
file='PipelinePart2_Plink2FilteringAlleles.sh')

# The following command is necessary to 
dos2unix('PipelinePart2_Plink2FilteringAlleles.sh')
```